---
title: "Two-Step Clustering-Based Bayesian Network Structure Learning (Full Version)"
author: "Yikun Zhang"
output: html_document
---

```{r}
library(bnlearn)
library(cluster)
library(ggplot2)
```


# Functional Programming of a cluster-based Bayesian network structure learning (Retain all the arcs in the clusters)
```{r}
cluster_BNL = function(data, stand = TRUE, method = "average", N = floor(sqrt(2)*ncol(data)/2), algo = gs, ...){
  # Functional programming of the two-step clustering-based Bayesian network structrue learning strategy. The function takes a data frame as an input. "stand" is a logical variable indicating whether a standization should be performed. "method" is used for the clustering. "N" tuned the number of groups into which the variables are divided.
  
  require(bnlearn)
  require(cluster)
  require(infotheo)
  
  if(names(as.list.function(algo))[2] == "start"){
    data1 = as.data.frame(lapply(data, as.numeric))
    if(stand){
      data1 = apply(data1, MARGIN = 2, function(column){
        column - mean(unique(column))
      })
      dissim = as.dist(matrix(1, nrow = ncol(data1), ncol = ncol(data1)) - cor(data1))
    }else{
      dissim = as.dist(matrix(1, nrow = ncol(data1), ncol = ncol(data1)) - cor(data1))
    }
  }else{
    
     if(all(sapply(data, class) == "factor")){
       dissim = as.dist(-mutinformation(data))
     }else if(all(sapply(data, class) == "numeric")){
       dissim = as.dist(matrix(1, nrow = ncol(data), ncol = ncol(data)) - cor(data))
     }else{
       data1 = as.data.frame(lapply(data, as.numeric))
       data1 = apply(data1, MARGIN = 2, function(column){
         column - mean(unique(column))
       })
       dissim = as.dist(matrix(1, nrow = ncol(data1), ncol = ncol(data1)) - cor(data1))
     }
  }
  
  dissim[is.na(dissim)] = 2
  cluster1 = agnes(dissim, diss = inherits(dissim, "dist"), stand = FALSE, method = method)
  Group = cutree(cluster1, k = N)

  whiteArcs = data.frame(from = c(), to = c())
  for(i in 1:N){
    index = (Group == i)
  
    if(sum(index) > 1){
      bn.cluster = algo(data[ ,index])
      whiteArcs = rbind(whiteArcs, bn.cluster$arcs)
    }
  }
  
  if(nrow(whiteArcs) == 0){
    whiteArcs = NULL
    bn.cl1 = algo(data, whitelist = whiteArcs)
    return(bn.cl1)
  }
  
  if(names(as.list.function(algo))[2] == "start"){
    init_net = empty.graph(names(data))
    arcs(init_net, check.cycles = FALSE) = as.matrix(whiteArcs)
    bn.cl1 = algo(data, start = init_net)
  }else{
    bn.cl1 = algo(data, whitelist = whiteArcs)
  }
  
  return(bn.cl1)
}
```


# Helper function: Compute the accuracy of the resulted Bayesian network
```{r}
ACC = function(actual, learning, n){
  # "actual" should be a data frame whose two column are "from" and "to". So does "learning".
  
  actual_arcs = paste(actual[,1], actual[,2])
  learning_arcs = paste(learning[,1], learning[,2])
  
  TP = length(intersect(actual_arcs, learning_arcs))
  TN = n*(n-1) - length(union(actual_arcs, learning_arcs))
  return((TP+TN)/(n*(n-1)))
}
```


# Experimental Results
## Accuracy Analysis (Embedding Different Methods)
```{r}
accuracy_anal = function(data_actual, algo = gs, n_run = 100, n_samples = 1000, ...){
  require(bnlearn)
  TSCB_acc = numeric(length = n_run)
  Tra_acc = numeric(length = n_run)
  actual_arcs = arcs(data_actual)
  
  for(i in 1:n_run){
    data = rbn(data_actual, n_samples)
    
    accuracy = numeric(ncol(data))
    for(j in 1:ncol(data)){
      re = NULL
      try((re = ACC(actual_arcs, learning = cluster_BNL(data, N = j, algo = algo)$arcs, n = ncol(data))), silent = T)
      if(is.null(re)){
        j = j-1
        break
      }else{
        accuracy[j] = re
      }
    }
    
    TSCB_acc[i] = max(accuracy)
    Tra_acc[i] = accuracy[ncol(data)]
  }
  record = data.frame(TSCB = TSCB_acc, Traditional = Tra_acc)
  return(record)
}

# Embed GS
# "alarm"
alarm_actual = readRDS("alarm.rds")
alarm_acc_gs = accuracy_anal(alarm_actual, algo = gs)

# "asia"
asia_actual = readRDS("asia.rds")
asia_acc_gs = accuracy_anal(asia_actual, algo = gs)

# "insurance" (Run Step-by-step)
insurance_actual = readRDS("insurance.rds")
insurance_acc_gs = accuracy_anal(insurance_actual, algo = gs)

# "hepar2"
hepar2_actual = readRDS("hepar2.rds")
hepar2_acc_gs = accuracy_anal(hepar2_actual, algo = gs)


# Embed IAMB
# "alarm"
alarm_acc_iamb = accuracy_anal(alarm_actual, algo = iamb)

# "asia"
asia_acc_iamb = accuracy_anal(asia_actual, algo = iamb)

# "insurance"
insurance_acc_iamb = accuracy_anal(insurance_actual, algo = iamb)

# "hepar2"
hepar2_acc_iamb = accuracy_anal(hepar2_actual, algo = iamb)


# Embed Iter-IAMB
# "alarm"
alarm_acc_inter_iamb = accuracy_anal(alarm_actual, algo = inter.iamb)

# "asia"
asia_acc_inter_iamb = accuracy_anal(asia_actual, algo = inter.iamb)

# "insurance"
insurance_acc_inter_iamb = accuracy_anal(insurance_actual, algo = inter.iamb)

# "hepar2"
hepar2_acc_inter_iamb = accuracy_anal(hepar2_actual, algo = inter.iamb)


# Embed MMPC
# "alarm"
alarm_acc_mmpc = accuracy_anal(alarm_actual, algo = mmpc)

# "asia"
asia_acc_mmpc = accuracy_anal(asia_actual, algo = mmpc)

# "insurance"
insurance_acc_mmpc = accuracy_anal(insurance_actual, algo = mmpc)

# "hepar2"
hepar2_acc_mmpc = accuracy_anal(hepar2_actual, algo = mmpc)


# Embed HC
# "alarm"
alarm_acc_hc = accuracy_anal(alarm_actual, algo = hc)

# "asia"
asia_acc_hc = accuracy_anal(asia_actual, algo = hc)

# "insurance"
insurance_acc_hc = accuracy_anal(insurance_actual, algo = hc)

# "hepar2"
hepar2_acc_hc = accuracy_anal(hepar2_actual, algo = hc)


# Embed TABU
# "alarm"
alarm_acc_tabu = accuracy_anal(alarm_actual, algo = tabu)

# "asia"
asia_acc_tabu = accuracy_anal(asia_actual, algo = tabu)

# "insurance"
insurance_acc_tabu = accuracy_anal(insurance_actual, algo = tabu)

# "hepar2"
hepar2_acc_tabu = accuracy_anal(hepar2_actual, algo = tabu)
```

## Accuracy Analysis on "alarm" dataset
```{r}
data(alarm)
Alarm = as.data.frame(lapply(alarm, as.factor))

modelstring = paste("[HIST|LVF][CVP|LVV][PCWP|LVV][HYP][LVV|HYP:LVF]",
  "[LVF][STKV|HYP:LVF][ERLO][HRBP|ERLO:HR][HREK|ERCA:HR][ERCA]",
  "[HRSA|ERCA:HR][ANES][APL][TPR|APL][ECO2|ACO2:VLNG][KINK]",
  "[MINV|INT:VLNG][FIO2][PVS|FIO2:VALV][SAO2|PVS:SHNT][PAP|PMB][PMB]",
  "[SHNT|INT:PMB][INT][PRSS|INT:KINK:VTUB][DISC][MVS][VMCH|MVS]",
  "[VTUB|DISC:VMCH][VLNG|INT:KINK:VTUB][VALV|INT:VLNG][ACO2|VALV]",
  "[CCHL|ACO2:ANES:SAO2:TPR][HR|CCHL][CO|HR:STKV][BP|CO:TPR]", sep = "")
Alarm_actual = model2network(modelstring)

# GS Algorithm
library(ggplot2)
Alarm_acc1 = numeric(ncol(Alarm))
for(i in 1:ncol(Alarm)){
  Alarm_acc1[i] = ACC(actual = Alarm_actual$arcs, learning = cluster_BNL(Alarm, N = i)$arcs, n = ncol(Alarm))
}
Alarm_acc1 = data.frame(NG = 1:ncol(Alarm), Accuracy = Alarm_acc1)

ggplot(Alarm_acc1, mapping = aes(NG, Accuracy)) + geom_hline(yintercept = Alarm_acc1$Accuracy[nrow(Alarm_acc1)], color = "black", size = 1, linetype = 2) + geom_point(size = 2, shape = 2) + geom_line(color = "red", size = 0.8) + labs(x = "", y = "Accuracy") + theme_bw() + theme(panel.border = element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"), axis.title = element_text(size = 25), axis.text = element_text(size = 20))

# hill-climbing algorithm

library(ggplot2)
Alarm_acc2 = numeric(ncol(Alarm))
for(i in 1:ncol(Alarm)){
  Alarm_acc2[i] = ACC(actual = Alarm_actual$arcs, learning = cluster_BNL(Alarm, N = i, algo = hc)$arcs, n = ncol(Alarm))
}
Alarm_acc2 = data.frame(NG = 1:ncol(Alarm), Accuracy = Alarm_acc2)

ggplot(Alarm_acc2, mapping = aes(NG, Accuracy)) + geom_hline(yintercept = Alarm_acc2$Accuracy[nrow(Alarm_acc2)], color = "black", size = 1, linetype = 2) + geom_point(size = 2, shape = 1) + geom_line(color = "blue", size = 0.8) + labs(x = "The Number of Clusters", y = "Accuracy") + theme_bw() + theme(panel.border = element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"), axis.title = element_text(size = 25), axis.text = element_text(size = 20))


# Plot the network configuration (Use the fast version)
graphviz.compare(Alarm_actual, cluster_BNL(Alarm, N = which.max(Alarm_acc1$Accuracy)), gs(Alarm), diff.args = list(fp.col = "red", fp.lty = "dotted",fp.lwd = 3, fn.col = "blue", fn.lty = "longdash", fn.lwd = 1.5), layout = "dot", shape = "ellipse")
```


# Time Efficiency Analysis
## Fast version for TSCB strategy
```{r}
cluster_BNL = function(data, stand = TRUE, method = "average", N = floor(sqrt(2)*ncol(data)/2), algo = gs, ...){
  # Functional programming of the cluster-based Bayesian network structrue learning. The function takes a data frame as an input. "stand" is a logical variable indicating whether a standization should be performed. "method" is used for the clustering. "N" tuned the number of groups into which the variables are divided.
  
  require(bnlearn)
  require(cluster)
  
  if(sum(sapply(data, class) != "factor") > 0) stop("The class of the data frame should be factor!")
  
  data1 = as.data.frame(lapply(data, as.numeric))
  if(stand & any(sapply(data, class) == "factor")){
    data1 = apply(data1, MARGIN = 2, function(column){
      column - mean(unique(column))
    })
    dissim = as.dist(matrix(1, nrow = ncol(data1), ncol = ncol(data1)) - cor(data1))
  }else{
    dissim = as.dist(matrix(1, nrow = ncol(data1), ncol = ncol(data1)) - cor(data1))
  }
  
  dissim[is.na(dissim)] = 2
  cluster1 = agnes(dissim, diss = inherits(dissim, "dist"), stand = FALSE, method = method)
  Group = cutree(cluster1, k = N)

  whiteArcs = data.frame(from = c(), to = c())
  for(i in 1:N){
    index = (Group == i)
  
    if(sum(index) > 1){
      bn.cluster = algo(data[ ,index])
      whiteArcs = rbind(whiteArcs, bn.cluster$arcs)
    }
  }
  
  if(nrow(whiteArcs) == 0){
    whiteArcs = NULL
    bn.cl1 = algo(data, whitelist = whiteArcs)
    return(bn.cl1)
  }
  
  if(names(as.list.function(algo))[2] == "start"){
    init_net = empty.graph(names(data))
    arcs(init_net, check.cycles = FALSE) = as.matrix(whiteArcs)
    bn.cl1 = algo(data, start = init_net, whitelist = whiteArcs)
  }else{
    bn.cl1 = algo(data, whitelist = whiteArcs)
  }
  
  return(bn.cl1)
}
```


## Calculate the running time in each step
```{r}
time_step = function(data, stand = TRUE, method = "average", N = floor(sqrt(2)*ncol(data)/2), algo = hc, n_run = 100, ...){
  require(bnlearn)
  require(cluster)
  
  time_elapsed = matrix(0, ncol = 3, nrow = n_run)
  time_elapsed = apply(time_elapsed, MARGIN = 1, function(Time){
    
    Time[1] = system.time({
      data1 = as.data.frame(lapply(data, as.numeric))
  data1 = apply(data1, MARGIN = 2, function(column){
      column - mean(unique(column))
    })
      dissim = as.dist(matrix(1, nrow = ncol(data1), ncol = ncol(data1)) - cor(data1))
      dissim[is.na(dissim)] = 2
      cluster1 = agnes(dissim, diss = inherits(dissim, "dist"), stand = FALSE, method = method)
      Group = cutree(cluster1, k = N)
    })[3]
    
    Time[2] = system.time({
      whiteArcs = data.frame(from = c(), to = c())
      for(i in 1:N){
         index = (Group == i)
  
         if(sum(index) > 1){
            bn.cluster = algo(data[ ,index])
            whiteArcs = rbind(whiteArcs, bn.cluster$arcs)
         } 
       }
    })[3]
    
    Time[3] = system.time({
      if(nrow(whiteArcs) == 0) whiteArcs = NULL
      bn.cl1 = algo(data, whitelist = whiteArcs)
    })[3]
    return(Time)
  })
  time_elapsed = t(time_elapsed)
  colnames(time_elapsed) = c("cluster", "learn_in_cluster", "combine")
  return(time_elapsed)
}

# "alarm" data set
alarm_actual = readRDS("alarm.rds")
t_alarm1 = data.frame()
for(i in 1:50){
  data = rbn(alarm_actual, 2000)
  
  acc1 = numeric(ncol(data))
  for(i in 1:ncol(data)){
    acc1[i] = ACC(actual = arcs(alarm_actual), learning = cluster_BNL(data, N = i, algo = gs)$arcs, n = ncol(data))
  }
  
  t50 = time_step(data, algo = gs, n_run = 10, N = which.max(acc1))
  t50 = as.data.frame(t50)
  t50$tra = sapply(rep(0, 10), function(t){
    return(system.time(gs(data))[3])
  })
  
  t_alarm1 = rbind(t_alarm1, sapply(t50, mean))
}
colnames(t_alarm1) = c("cluster", "learn_in_cluster", "combine", "tra")

# "asia" data set
asia_actual = readRDS("asia.rds")
t_asia1 = data.frame()
for(i in 1:50){
  data = rbn(asia_actual, 2000)
  
  acc1 = numeric(ncol(data))
  for(i in 1:ncol(data)){
    acc1[i] = ACC(actual = arcs(asia_actual), learning = cluster_BNL(data, N = i, algo = gs)$arcs, n = ncol(data))
  }
  
  t50 = time_step(data, algo = gs, n_run = 10, N = which.max(acc1))
  t50 = as.data.frame(t50)
  t50$tra = sapply(rep(0, 10), function(t){
    return(system.time(gs(data))[3])
  })
  
  t_asia1 = rbind(t_asia1, sapply(t50, mean))
}
colnames(t_asia1) = c("cluster", "learn_in_cluster", "combine", "tra")

# "insurance" data set
insurance_actual = readRDS("insurance.rds")
t_insurance1 = data.frame()
for(i in 1:50){
  data = rbn(insurance_actual, 2000)

  acc1 = numeric(ncol(data))
  for(j in 1:ncol(data)){
    try((acc1[j] = ACC(actual = arcs(insurance_actual), learning = cluster_BNL(data, N = j, algo = gs)$arcs, n = ncol(data))), silent = TRUE)
    if(acc1[j]){
      j = j-1
      break
    }
  }

  t50 = time_step(data, algo = gs, n_run = 10, N = which.max(acc1))
  t50 = as.data.frame(t50)
  t50$tra = sapply(rep(0, 10), function(t){
    return(system.time(gs(data))[3])
  })

  t_insurance1 = rbind(t_insurance1, sapply(t50, mean))
}
colnames(t_insurance1) = c("cluster", "learn_in_cluster", "combine", "tra")

# "hepar2" data set
hepar2_actual = readRDS("hepar2.rds")
t_hepar21 = data.frame()
for(i in 1:50){
  data = rbn(hepar2_actual, 5000)
  
  acc1 = numeric(ncol(data)-9)
  for(i in 10:ncol(data)){
    acc1[i-9] = ACC(actual = arcs(hepar2_actual), learning = cluster_BNL(data, N = i, algo = gs)$arcs, n = ncol(data))
  }
  
  t50 = time_step(data, algo = gs, n_run = 10, N = which.max(acc1)+9)
  t50 = as.data.frame(t50)
  t50$tra = sapply(rep(0, 10), function(t){
    return(system.time(gs(data))[3])
  })
  
  t_hepar21 = rbind(t_hepar21, sapply(t50, mean))
}
colnames(t_hepar21) = c("cluster", "learn_in_cluster", "combine", "tra")
```


## Time Analysis on "alarm" Dataset
### Time Variation on "alarm"
```{r}
time_comparison1 = function(data, kmax, algo = gs, meth = cluster_BNL, n_run = 100, meth_index = NULL){
  
    if(is.null(meth_index)) meth_index = "Retain all arcs"
    
  if(meth_index == "Tra"){
    time_elapsed = numeric(length = n_run)
    time_elapsed = sapply(time_elapsed, function(x){
      return(system.time(algo(data))[3])
    })
  }else{
    time_elapsed = numeric(length = n_run)
    time_elapsed = sapply(time_elapsed, function(x){
      return(system.time(meth(data, N = kmax, algo = algo))[3])
    })
  }
  
  time_com = data.frame(time = time_elapsed, group = rep(meth_index, n_run), Kindex = rep(kmax, n_run))
  
  return(time_com)
}

data(alarm)
Alarm = as.data.frame(lapply(alarm, as.factor))
t_gs = data.frame()
for(i in 1:ncol(Alarm)){
  if(i == ncol(Alarm)){
    t_gs = rbind(t_gs, time_comparison1(Alarm, kmax = i, algo = gs, n_run = 200, meth_index = "Tra"))
  }else{
    t_gs = rbind(t_gs, time_comparison1(Alarm, kmax = i, algo = gs, n_run = 200, meth = cluster_BNL))
  }
}

t_gs1 = t_gs
t_gs1$group = as.character(t_gs1$group)
t_gs1[t_gs1$Kindex == "37", ]$group = "Traditional Method"
t_gs1$group = as.factor(t_gs1$group)
t_gs1$Kindex = as.factor(t_gs1$Kindex)
ggplot(t_gs1, mapping = aes(x = Kindex, y = time, color = group)) + geom_boxplot() + scale_color_manual(name = "", labels = c("TSCB", "Traditional Method"), values = c("cyan3", "black")) + labs(x = "The Number of Clusters", y = "Time (Sec)")  + theme_bw() + theme(panel.border = element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"), legend.position = c(0.8,0.85), axis.title = element_text(size = 45), axis.text.y = element_text(size = 25), axis.text.x = element_text(size = 15), legend.text = element_text(size = 30))
```

## Time Comparison of different methods
```{r}
modelstring = paste("[HIST|LVF][CVP|LVV][PCWP|LVV][HYP][LVV|HYP:LVF]",
  "[LVF][STKV|HYP:LVF][ERLO][HRBP|ERLO:HR][HREK|ERCA:HR][ERCA]",
  "[HRSA|ERCA:HR][ANES][APL][TPR|APL][ECO2|ACO2:VLNG][KINK]",
  "[MINV|INT:VLNG][FIO2][PVS|FIO2:VALV][SAO2|PVS:SHNT][PAP|PMB][PMB]",
  "[SHNT|INT:PMB][INT][PRSS|INT:KINK:VTUB][DISC][MVS][VMCH|MVS]",
  "[VTUB|DISC:VMCH][VLNG|INT:KINK:VTUB][VALV|INT:VLNG][ACO2|VALV]",
  "[CCHL|ACO2:ANES:SAO2:TPR][HR|CCHL][CO|HR:STKV][BP|CO:TPR]", sep = "")
Alarm_actual = model2network(modelstring)

acc_al_op = data.frame(TSCB = rep(0, 6), traditional = rep(0, 6))
acc_al_op$TSCB = sapply(c(gs, iamb, inter.iamb, mmpc, hc, tabu), function(algorithm){
  
  acc1 = numeric(length = ncol(Alarm))
  for(i in 1:ncol(Alarm)){
    acc1[i] = ACC(actual = Alarm_actual$arcs, learning = cluster_BNL(alarm, algo = algorithm, N = i)$arcs, n = ncol(alarm))
  }
  
  n_max = which.max(acc1)
  
  return(ACC(actual = Alarm_actual$arcs, learning = cluster_BNL(alarm, algo = algorithm, N = n_max)$arcs, n = ncol(alarm)))
})

acc_al_op$optimal_K = sapply(c(gs, iamb, inter.iamb, mmpc, hc, tabu), function(algorithm){
  acc1 = numeric(length = ncol(Alarm))

  for(i in 1:ncol(Alarm)){
    acc1[i] = ACC(actual = Alarm_actual$arcs, learning = cluster_BNL(alarm, algo = algorithm, N = i)$arcs, n = ncol(alarm))
  }

  return(which.max(acc1))
})

acc_al_op$traditional = sapply(c(gs, iamb, inter.iamb, mmpc, hc, tabu), function(algorithm){
  return(ACC(Alarm_actual$arcs, learning = algorithm(alarm)$arcs, n = ncol(alarm)))
})

acc_al_op$Method = c("gs", "iamb", "inter.iamb", "mmpc", "hc", "tabu")



time_comparison1 = function(data, kmax, algo = gs, n_run = 100, meth_index = NULL){
  
    meth = cluster_BNL
    if(is.null(meth_index)) meth_index = "Retain all arcs"
  
  time_elapsed = numeric(length = n_run)
  time_elapsed = sapply(time_elapsed, function(x){
    return(system.time(meth(data, N = kmax, algo = algo))[3])
  })
  
  time_com = data.frame(time = time_elapsed, group = rep(meth_index, n_run), Kindex = rep(kmax, n_run))
  
  return(time_com)
}

result = data.frame()
algorithm = c(gs, iamb, inter.iamb, mmpc, hc, tabu)

for(i in 1:6){
  Time = time_comparison1(alarm, kmax = acc_al_op$optimal_K[i], algo = algorithm[[i]], n_run = 200)$time
  time_tra = sapply(rep(0, 200), function(t){
  return(system.time(algorithm[[i]](Alarm))[3])
})
  Time = c(Time, time_tra)
  
  result = rbind(result, data.frame(Time, group = c(rep("Retain all arcs", 200), rep("Traditional Method", 200)), Kindex = rep(acc_al_op$optimal_K[i], 200)))
}

result$Method = rep(c("gs", "iamb", "inter.iamb", "mmpc", "hc", "tabu"), each = 400)

ggplot(result) + geom_boxplot(mapping = aes(x = Method, y = Time, color = group)) + scale_color_manual(name = "", labels = c("TSCB", "Traditional Methods"), values = c("cyan3", "black")) + labs(x = "Traditional Methods", y = "Time (Sec)")  + theme_bw() + theme(panel.border = element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"), legend.position = c(0.8,0.9), axis.title = element_text(size = 45), axis.text = element_text(size = 28), legend.text = element_text(size = 29))
```


## Combine TSCB strategy of constraint-based methods with score-based algorithms
```{r}
data(alarm)
Alarm = as.data.frame(lapply(alarm, as.factor))

modelstring = paste("[HIST|LVF][CVP|LVV][PCWP|LVV][HYP][LVV|HYP:LVF]",
  "[LVF][STKV|HYP:LVF][ERLO][HRBP|ERLO:HR][HREK|ERCA:HR][ERCA]",
  "[HRSA|ERCA:HR][ANES][APL][TPR|APL][ECO2|ACO2:VLNG][KINK]",
  "[MINV|INT:VLNG][FIO2][PVS|FIO2:VALV][SAO2|PVS:SHNT][PAP|PMB][PMB]",
  "[SHNT|INT:PMB][INT][PRSS|INT:KINK:VTUB][DISC][MVS][VMCH|MVS]",
  "[VTUB|DISC:VMCH][VLNG|INT:KINK:VTUB][VALV|INT:VLNG][ACO2|VALV]",
  "[CCHL|ACO2:ANES:SAO2:TPR][HR|CCHL][CO|HR:STKV][BP|CO:TPR]", sep = "")
Alarm_actual = model2network(modelstring)



library(ggplot2)
alarm_acc2 = numeric(ncol(alarm))
for(i in 1:ncol(alarm)){
  bn.combine = cluster_BNL(Alarm, algo = gs, N = i)
  undirect_arcs = undirected.arcs(bn.combine)
  undirect_arcs1 = apply(undirect_arcs, MARGIN = 1, function(item){
    return(paste(item[1], item[2]))
  })
  arcs1 = apply(bn.combine$arcs, MARGIN = 1, function(item){
    return(paste(item[1], item[2]))
  })
  bn.combine$arcs = bn.combine$arcs[!(arcs1 %in% undirect_arcs1), ]
  bn.combine = hc(alarm, start = bn.combine)
  
  alarm_acc2[i] = ACC(actual = Alarm_actual$arcs, learning = bn.combine$arcs, n = ncol(alarm))
}
alarm_acc22 = data.frame(NG = 1:ncol(alarm), Accuracy = c(alarm_acc2, Alarm_acc1$Accuracy, Alarm_acc2$Accuracy), class = as.factor(rep(c("Combine", "TSCB", "HC"), each = ncol(Alarm))))

ggplot(alarm_acc22, mapping = aes(NG, Accuracy, color = class, shape = class, linetype = class)) + geom_hline(yintercept = Alarm_acc1$Accuracy[nrow(Alarm_acc1)], color = "black", size = 2, linetype = 2) + geom_point(size = 4) + geom_line(size = 1.3) + labs(x = "The Number of Clusters", y = "Accuracy") + scale_shape_discrete(name = "", labels = c("Combined TSCB and HC", "TSCB With GS", "HC With TSCB")) + scale_color_discrete(breaks = NULL) + scale_linetype_discrete(breaks = NULL) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), axis.title = element_text(size = 25), axis.text = element_text(size = 20), legend.position = c(0.2, 0.9), legend.text = element_text(size = 20))


accuracy_combine = function(data_actual, algo1 = "gs", algo2 = "hc", n_run = 50, n_samples = 1000, ...){
  require(bnlearn)
  Tra1_acc = numeric(length = n_run)
  Tra2_acc = numeric(length = n_run)
  TSCB_acc = numeric(length = n_run)
  Combine_acc = numeric(length = n_run)
  actual_arcs = arcs(data_actual)
  
  for(i in 1:n_run){
    data = rbn(data_actual, n_samples)
    
    accuracy1 = numeric(ncol(data))
    accuracy2 = numeric(ncol(data))
    flag = 0
    
    for(j in 1:ncol(data)){
      bn_1 = cluster_BNL(data, N = j, algo = get(algo1))
      undi_arcs = undirected.arcs(bn_1)
      if(length(undi_arcs)){
        undi_arcs1 = apply(undi_arcs, MARGIN = 1, function(item){
          return(paste(item[1], item[2]))
        })
        arcs1 = apply(bn_1$arcs, MARGIN = 1, function(item){
          return(paste(item[1], item[2]))
        })
        bn_1$arcs = bn_1$arcs[!(arcs1 %in% undi_arcs1), ]
      }
      re = NULL
      try((re = bn.combine = get(algo2)(data, start = bn_1)), silent = TRUE)
      if(is.null(re)){
        flag = 1
        break
      }
      accuracy1[j] = ACC(actual_arcs, learning = cluster_BNL(data, N = j, algo = get(algo1))$arcs, n = ncol(data))
      accuracy2[j] = ACC(actual_arcs, learning = bn.combine$arcs, n = ncol(data))
    }
    if(flag){
      i = i-1
      break
    }
    TSCB_acc[i] = max(accuracy1)
    Tra1_acc[i] = accuracy1[ncol(data)]
    Tra2_acc[i] = ACC(actual_arcs, learning = get(algo2)(data)$arcs, n = ncol(data))
    Combine_acc[i] = max(accuracy2)
  }
  record = data.frame(Tra1_acc, Tra2_acc, TSCB_acc, Combine_acc)
  names(record) = c(algo1, algo2, "TSCB", "Combine")
  return(record)
}


# Embed GS, HC
# "alarm"
alarm_actual = readRDS("alarm.rds")
alarm_acc_gs_hc = accuracy_combine(alarm_actual, algo1 = "gs", algo2 = "hc")

# "asia"
asia_actual = readRDS("asia.rds")
asia_acc_gs_hc = accuracy_combine(asia_actual, algo1 = "gs", algo2 = "hc")

# "insurance"
insurance_actual = readRDS("insurance.rds")
insurance_acc_gs_hc = accuracy_combine(insurance_actual, algo1 = "gs", algo2 = "hc")

# "hepar2"
hepar2_actual = readRDS("hepar2.rds")
hepar2_acc_gs_hc = accuracy_combine(hepar2_actual, algo1 = "gs", algo2 = "hc")


# Embed IAMB, HC
# "alarm"
alarm_acc_iamb_hc = accuracy_combine(alarm_actual, algo1 = "iamb", algo2 = "hc")

# "asia"
asia_acc_iamb_hc = accuracy_combine(asia_actual, algo1 = "iamb", algo2 = "hc")

# "insurance"
insurance_acc_iamb_hc = accuracy_combine(insurance_actual, algo1 = "iamb", algo2 = "hc")

# "hepar2"
hepar2_acc_iamb_hc = accuracy_combine(hepar2_actual, algo1 = "iamb", algo2 = "hc")


# Embed inter-IAMB, HC
# "alarm"
alarm_acc_inter_IAMB_hc = accuracy_combine(alarm_actual, algo1 = "inter.iamb", algo2 = "hc")

# "asia"
asia_acc_inter_IAMB_hc = accuracy_combine(asia_actual, algo1 = "inter.iamb", algo2 = "hc")

# "insurance"
insurance_acc_inter_IAMB_hc = accuracy_combine(insurance_actual, algo1 = "inter.iamb", algo2 = "hc")

# "hepar2"
hepar2_acc_inter_IAMB_hc = accuracy_combine(hepar2_actual, algo1 = "inter.iamb", algo2 = "hc")


# Embed MMPC, HC
# "alarm"
alarm_acc_mmpc_hc = accuracy_combine(alarm_actual, algo1 = "mmpc", algo2 = "hc")

# "asia"
asia_acc_mmpc_hc = accuracy_combine(asia_actual, algo1 = "mmpc", algo2 = "hc")

# "insurance"
insurance_acc_mmpc_hc = accuracy_combine(insurance_actual, algo1 = "mmpc", algo2 = "hc")

# "hepar2"
hepar2_acc_mmpc_hc = accuracy_combine(hepar2_actual, algo1 = "mmpc", algo2 = "hc")


# Embed GS, TABU
# "alarm"
alarm_acc_gs_tabu = accuracy_combine(alarm_actual, algo1 = "gs", algo2 = "tabu")

# "asia"
asia_acc_gs_tabu = accuracy_combine(asia_actual, algo1 = "gs", algo2 = "tabu")

# "insurance"
insurance_acc_gs_tabu = accuracy_combine(insurance_actual, algo1 = "gs", algo2 = "tabu")

# "hepar2"
hepar2_acc_gs_tabu = accuracy_combine(hepar2_actual, algo1 = "gs", algo2 = "tabu")


# Embed IAMB, TABU
# "alarm"
alarm_acc_iamb_tabu = accuracy_combine(alarm_actual, algo1 = "iamb", algo2 = "tabu")

# "asia"
asia_acc_iamb_tabu = accuracy_combine(asia_actual, algo1 = "iamb", algo2 = "tabu")

# "insurance"
insurance_acc_iamb_tabu = accuracy_combine(insurance_actual, algo1 = "iamb", algo2 = "tabu")

# "hepar2"
hepar2_acc_iamb_tabu = accuracy_combine(hepar2_actual, algo1 = "iamb", algo2 = "tabu")


# Embed inter-IAMB, TABU
# "alarm"
alarm_acc_inter_IAMB_tabu = accuracy_combine(alarm_actual, algo1 = "inter.iamb", algo2 = "tabu")

# "asia"
asia_acc_inter_IAMB_tabu = accuracy_combine(asia_actual, algo1 = "inter.iamb", algo2 = "tabu")

# "insurance"
insurance_acc_inter_IAMB_tabu = accuracy_combine(insurance_actual, algo1 = "inter.iamb", algo2 = "tabu")

# "hepar2"
hepar2_acc_inter_IAMB_tabu = accuracy_combine(hepar2_actual, algo1 = "inter.iamb", algo2 = "tabu")


# Embed MMPC, TABU
# "alarm"
alarm_acc_mmpc_tabu = accuracy_combine(alarm_actual, algo1 = "mmpc", algo2 = "tabu")

# "asia"
asia_acc_mmpc_tabu = accuracy_combine(asia_actual, algo1 = "mmpc", algo2 = "tabu")

# "insurance"
insurance_acc_mmpc_tabu = accuracy_combine(insurance_actual, algo1 = "mmpc", algo2 = "tabu")

# "hepar2"
hepar2_acc_mmpc_tabu = accuracy_combine(hepar2_actual, algo1 = "mmpc", algo2 = "tabu")



# Time Experiments
time_comparison_com = function(data, kmax, algo1 = "gs", algo2 = "hc", n_run = 100, meth_index = NULL){
  
    if(is.null(meth_index)) meth_index = "Combined"
    
  if(meth_index == "Tra"){
    time_elapsed = numeric(length = n_run)
    time_elapsed = sapply(time_elapsed, function(x){
      return(system.time(get(algo1)(data))[3])
    })
  }else{
    time_elapsed = numeric(length = n_run)
    time_elapsed = sapply(time_elapsed, function(x){
      return(system.time({
        bn_1 = cluster_BNL(data, N = kmax, algo = get(algo1))
        undi_arcs = undirected.arcs(bn_1)
        undi_arcs1 = apply(undi_arcs, MARGIN = 1, function(item){
          return(paste(item[1], item[2]))
        })
        arcs1 = apply(bn_1$arcs, MARGIN = 1, function(item){
          return(paste(item[1], item[2]))
        })
        # Discard the undirected edges
        bn_1$arcs = bn_1$arcs[!(arcs1 %in% undi_arcs1), ]
        bn.combine = get(algo2)(data, start = bn_1)
      })[3])
    })
  }
  
  time_com = data.frame(time = time_elapsed, group = rep(meth_index, n_run), Kindex = rep(kmax, n_run))
  
  return(time_com)
}

data(alarm)
Alarm = as.data.frame(lapply(alarm, as.factor))
t_com = data.frame()
for(i in 1:ncol(Alarm)){
  if(i == ncol(Alarm)){
    t_com = rbind(t_com, time_comparison_com(Alarm, kmax = i, algo1 = "gs", n_run = 100, meth_index = "Tra"))
  }else{
    t_com = rbind(t_com, time_comparison_com(Alarm, kmax = i, algo1 = "gs", algo2 = "hc", n_run = 100))
  }
}

t_com1 = t_com
t_com1$group = as.character(t_com1$group)
t_com1[t_com1$Kindex == "37", ]$group = "GS"
t_com1$group = as.factor(t_com1$group)
t_com1$Kindex = as.factor(t_com1$Kindex)
ggplot(t_com1, mapping = aes(x = Kindex, y = time, color = group)) + geom_boxplot() + scale_color_manual(name = "", labels = c("Combine", "Pure GS"), values = c("cyan3", "black")) + labs(x = "The Number of Clusters", y = "Time (Sec)")  + theme_bw() + theme(panel.border = element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"), legend.position = c(0.8,0.85), axis.title = element_text(size = 45), axis.text.y = element_text(size = 25), axis.text.x = element_text(size = 15), legend.text = element_text(size = 30))


# Comparing different methods

al_op_K = data.frame(accuracy = rep(0, 8), op_K = rep(0, 8), method = c("gs_hc", "iamb_hc", "inter.iamb_hc", "mmpc_hc", "gs_tabu", "iamb_tabu", "inter.iamb_tabu", "mmpc_tabu"), stringsAsFactors = FALSE)
for(i in 1:8){
  algo1 = strsplit(al_op_K$method[i], split = "_")[[1]][1]
  algo2 = strsplit(al_op_K$method[i], split = "_")[[1]][2]
  
  acc = numeric(length = ncol(Alarm))
  for(j in 1:ncol(Alarm)){
    bn_1 = cluster_BNL(Alarm, N = j, algo = get(algo1))
        undi_arcs = undirected.arcs(bn_1)
        undi_arcs1 = apply(undi_arcs, MARGIN = 1, function(item){
          return(paste(item[1], item[2]))
        })
        arcs1 = apply(bn_1$arcs, MARGIN = 1, function(item){
          return(paste(item[1], item[2]))
        })
        # Discard the undirected edges
        bn_1$arcs = bn_1$arcs[!(arcs1 %in% undi_arcs1), ]
        bn.combine = get(algo2)(Alarm, start = bn_1)
        acc[j] = ACC(Alarm_actual$arcs, learning = bn.combine$arcs, n = ncol(Alarm))
  }
  al_op_K$accuracy[i] = max(acc)
  if(sum(acc == max(acc)) > 1 & which.max(acc) < 10){
    al_op_K$op_K[i] = which(acc == max(acc))[which.min(abs(which(acc == max(acc))-mean(1:ncol(Alarm))))]
  }else{
    al_op_K$op_K[i] = which.max(acc)
  }
}



Ntimes = 200
result_com = data.frame()
meth = c("gs_hc", "iamb_hc", "inter.iamb_hc", "mmpc_hc", "gs_tabu", "iamb_tabu", "inter.iamb_tabu", "mmpc_tabu")

for(i in 1:8){
  algo1 = strsplit(meth[i], split = "_")[[1]][1]
  algo2 = strsplit(meth[i], split = "_")[[1]][2]
  
  Time = sapply(rep(0, Ntimes), function(t){
    return(system.time({
      bn_1 = cluster_BNL(Alarm, N = al_op_K$op_K[i], algo = get(algo1))
      undi_arcs = undirected.arcs(bn_1)
      undi_arcs1 = apply(undi_arcs, MARGIN = 1, function(item){
        return(paste(item[1], item[2]))
      })
      arcs1 = apply(bn_1$arcs, MARGIN = 1, function(item){
        return(paste(item[1], item[2]))
      })
      bn_1$arcs = bn_1$arcs[!(arcs1 %in% undi_arcs1), ]
      bn.combine = get(algo2)(Alarm, start = bn_1)
    })[3])
  })
  time_tra = sapply(rep(0, Ntimes), function(t){
    return(system.time(get(algo1)(Alarm))[3])
  })
  Time = c(Time, time_tra)
  
  result_com = rbind(result_com, data.frame(Time, group = c(rep("Combine", Ntimes), rep("Embedded Method", Ntimes)), Kindex = rep(al_op_K$op_K[i], Ntimes)))
}

result_com$Method = rep(meth, each = 2*Ntimes)

ggplot(result_com) + geom_boxplot(mapping = aes(x = Method, y = Time, color = group)) + scale_color_manual(name = "", labels = c("Combine", "Embedded Methods"), values = c("cyan3", "black")) + labs(x = "Embedded Methods", y = "Time (Sec)")  + theme_bw() + theme(panel.border = element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"), legend.position = c(0.8,0.9), axis.title = element_text(size = 45), axis.text = element_text(size = 28), legend.text = element_text(size = 29))
```
